How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
Removed double spaces
discussion update

\section{Discussion}
\label{sec:discussion}
\subsection{Implications}
Our results have some interesting implications for designers of educational programming languages.

\subsubsection{Popularity of Different Block Types}
Our analysis shows that some categories of blocks are rarely used, like the `Pen' blocks, of which only 194,885 occur within 19,090 (8.17\% of the total) programs. When further evolving the Scratch programming language, this category might be less important to users, and hence our current analysis supports the language designers in making future investments.

@@

\subsubsection{Exact Clones between Sprites}
With occurrences in 11\% of the Scratch projects in our dataset, the use of exactly identical clones between sprites is relatively common. In a sense, the Scratch users are not to blame here, as Scratch does not support procedure calls between sprites, only within them. So in many cases there is no other way to share the functionality than by making a copy. We are not aware of the underlying rationale of the Scratch team that lead to this decision, however it seems that a large part of the Scratch users would use the functionality to call procedures between sprites.

@@

\subsection{Threads to validity}
A thread to validity of this study is the fact that we did not scrap a random sample, but the most recent 250,000 projects. It could be the case that programming habits of Scratch users are changing over time. However, we counterbalanced that by using a very large dataset.

>>>>

\section{Discussion}
\label{sec:discussion}
\subsection{Implications}
We believe a large scale study of programs like ours can help language designers to tailor their language. In this section we highlight directions in which our study could support language design.

\subsubsection{Popularity of Different Block Types}
Our analysis shows that some categories of blocks are rarely used, like the `Pen' blocks, of which only 194,885 occur within 19,090 (8.17\% of the total) programs. Hence, in future changes to the language, `Pen' blocks might be less important to users to support or maintain.

@@

\subsubsection{Exact Clones Between Sprites}
With occurrences in 11\% of the Scratch projects in our dataset, the use of exactly identical clones between sprites is relatively common. In a sense, the Scratch users are not to blame here, as Scratch does not support procedure calls between sprites, only within them. So in many cases there is no other way to share the functionality than by making a copy. We are not aware of the underlying rationale of the Scratch team that lead to this decision, however it seems that a large part of the Scratch users would use the functionality to call procedures between sprites.

@@

\subsection{Threads to validity}
A thread to validity of this study is the fact that we did not scrape a random sample, but the most recent 250,000 projects. It could be the case that programming habits of Scratch users are changing over time. However, we counterbalanced that by using a large dataset which comprises of around 2\% of all 14 million shared Scratch programs.\footnote{\url{https://scratch.mit.edu/statistics/}}.
